What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-08 android-stacks.tex
smal change on a subsection title
changing CLU description

In languages such as CLU\footnote{In CLU,  if a handler is 
found for a given exception, it is converted in a predened default exception, 
called failure which is the only one which can be implicitly 
propagated in this model [ref-clue].}, Modula-3, Guide, and Extended Ada the exceptions are 
checked, which means that the 
compiler statically checks if appropriate handlers are provided within the system. 
Accordingly, the programmer must explicitly specify every exception that can be
signaled to support the compile time checking. This approach is known to be
costly to maintain (Dooren and Steegmans, 2005) since exception updates are
cascading; if a new exception type is added to a method signature then all other
methods directly using this method must either change their signatures to
include the new exception type or handle the new exception.

@@

In Java a method can throw either checked or unchecked exceptions. Java is the only language that allows a hybrid approach on which the developer can define exceptions of both kinds to be thrown and handled in a single system. Next section details Java exception handling model.

Although exception handling mechanism is the most used technique to deal with such 
failures - been embedded in several programming languages as show above,   
the exception handling code is often generally poorly understood and the least
tested part of software systems.This behaviour may lead to the problem of uncaught exceptions~\cite{jo2004uncaught}, one of the main causes of application crashes
(e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting, garcia2001comparative,cabral2007exception,coelho2011unveiling}).

@@

\subsubsection{Stack Traces on Issues}

@@

Programming errors are the causes of most of the exception stack traces reported
on issues. In the Android subset we could find more issues related to Backward
compatibility and security issues than on the general data set.

\subsection{Investigating Android Subset}

>>>>

In languages such as Modula-3, Guide, and Extended Ada the exceptions are 
checked, which means that the compiler statically checks if appropriate handlers are provided within the system. 
Accordingly, the programmer must explicitly specify every exception that can be
signaled to support the compile time checking. This approach is known to be
costly to maintain (Dooren and Steegmans, 2005) since exception updates are
cascading; if a new exception type is added to a method signature then all other
methods directly using this method must either change their signatures to
include the new exception type or handle the new exception.

@@

Both Java [ref: Gosling et al. 1996] and CLU [Liskov and Snyder 1979] support the declaration of exceptions
 in method signatures, hence the compiler can then check if handlers are provided to such exceptions.
 However, this support is only partial because both languages also provides a form of unchecked exceptions.
In CLU,  if a handler is found for a given exception, it is converted in a predened default exception, 
called failure which is the only one which can be implicitly propagated in this model [ref-clue].
 Java allows a hybrid approach on which the developer can define specific exceptions of both kinds 
(checked or unchecked) to be thrown and handled inside the system.
Therefore, in both languages the developer of a client module is not warned by the compiler of the possibility of 
an unchecked exception being thrown.

[REF]: Static Analysis to Support the Evolution of Exception Structure in Object-Oriented Systems

Although exception handling mechanism has been embedded in several programming languages 
as show above,   the exception handling code is often generally poorly understood and the least
tested part of software systems.

% This behaviour may lead to the problem of uncaught exceptions~\cite{jo2004uncaught}, one of the main causes of application crashes
%(e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting, garcia2001comparative,cabral2007exception,coelho2011unveiling}).

@@

\subsubsection{Exception Stack Traces on Issues}

@@

Programming errors are the causes of most of the exception stack traces reported
on issues both in  general Java data set and Android subset. In the Android subset we could find 
more stack traces reporting exceptions related to Backward
compatibility and security concerns than on the general data set.

TODO: Discuss about the interater agreement here...

\subsection{Investigating The Android Subset}
